Ternary plots for `hyper2` and `hyper3` samples

### 2024-10-18 inst/ternaryplot_hyper2.Rmd
observation about nature of MH sampling
consistentification

(takes about fifteen minutes to run without cache).

@@

Figures \@ref(fig:iconsmatplot) and \@ref(fig:selectjustbigones) show
different aspects of the BT strengths of the six icons of the `icons`
dataset.

>>>>

<font size="1"> (takes about fifteen minutes to run without cache)
</font>

@@

Figures \@ref(fig:iconsmatplot) and \@ref(fig:selectjustbigones) show
different aspects of the BT strengths of the six icons of the `icons`
dataset.  Note that figure \@ref(fig:selectjustbigones) is potentially
misleading: due to the sequential correlation of MH sampling, repeated
observations are overplotted and thus under-represented.
